---
title: "FNGr"
author: "Ben Williams"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FNGr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, error = FALSE, warning = FALSE,
  comment = "#>"
)
```

```{r}
library(FNGr)
library(tidyverse)
library(scales)
theme_set(theme_sleek())

data.frame(year = 1973:2017, age = 1:5) %>%
  mutate(y = rnorm(n(), 10,5)) -> df
```


  The basic ggplot figure spaces years about every 5-10, depending on the timeseries length.

```{r}
ggplot(df, aes(year, age, size = y)) + geom_point()  + scale_size_area()
```
  This makes for a rather poor axis, for our typical presentation needs.
  We can clean this up somewhat by using breaks or the pretty_breaks function from the scales package
```{r}
ggplot(df, aes(year, age, size = y)) + geom_point() + scale_size_area() +
    scale_x_continuous(breaks = seq(1973, 2016, 3))

ggplot(df, aes(year, age, size = y)) + geom_point() +
  scale_x_continuous(breaks = pretty_breaks(n = 15))
```
  However this does not show a tick for each year, something that has been regularly requested.
  tickr will add a tick mark to each year and provide a label for the interval designated.

Labels every 10 years.
```{r}
xaxis = tickr(df, year, 10)
yaxis = tickr(df, age, 2)

ggplot(df, aes(year, age, size = y)) + geom_point() +
  scale_x_continuous(breaks = xaxis$breaks, labels = xaxis$labels) +
  scale_y_continuous(breaks = yaxis$breaks, labels = yaxis$labels)
```
